Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-10 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:10	15:36:48	(Mon10.Aug)

@@

% - How much oversampling
% - How many parameters, how great a span.
% 
% - Experiemental data, Holmengraa/cross
% 
% - Note on efficiency.

From our work with MVDR it

Traditionally beamformers were static, but as processors get more powerful so with the emergence of more processing power

@@

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
f_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{2m}{M-1}-1\right)^2}\right)}{I_0(\pi\beta)}, & 0\le m\le M-1 \\
0 & \text{otherwise},
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind:
%
\begin{align}
I_0(x) = \sumb{a=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^a}{a!} \right]^2.
\end{align}
%
The Kaiser-Bessel window is near optimal in the sense of having its peak energy concentration around $\theta=0^\circ$, for a time-bandwidth product specified with the parameter $\beta$:
%
\begin{align}
\beta = \frac{TB}{2},
\end{align}
%
where $T$ is the extent of the window in time and $B$ is its bandwidth. Adjusting $\beta$ changes the trade-off between mainlobe width and sidelobe level. At small values the windows approach the response of a rectangular window, and at large values ($>5$) the window converges to a Gaussian both in time and frequency. This class of windows is generally considered well suited for separating closely spaced sources with amplitudes of a high dynamic range~\cite{Harris1978}, they are easy to make, and they are optimal for any value of $\beta$.

Before we apply the window to the sensor data, we normalize it to ensure unit gain in the direction of interest:
\begin{align}
\w = \frac{\vec f}{\f\T\1} \quad\quad\text{where}\quad\quad \f =
\bmat{
f_0 \\ \vdots \\ f_{M-1}                                                           
}
\end{align}

Note that the normalization factor $\f\T\1$ is the reciprocal of the window's coherent gain. Since the signal-to-noise ratio is constant for a given window, the effect of gaining the coherent signal by also allowing an equivalent incoherent noise gain.

>>>>

- Why?

@@

% - How much oversampling
% - How many parameters, how great a span.
% 
% - Experiemental data, Holmengraa/cross
% 
% - Note on efficiency.
% 
% 
% From our work with MVDR it 
% 
% 
% Traditionally beamformers were static, but as processors get more powerful so with the emergence of more processing power

@@

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
f_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{2m}{M-1}-1\right)^2}\right)}{I_0(\pi\beta)}, & 0\le m\le M-1 \\
0 & \text{otherwise},
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind:
%
\begin{align}
I_0(x) = \sumb{a=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^a}{a!} \right]^2.
\end{align}
%
The Kaiser-Bessel window is near optimal in the sense of having its peak energy concentration around $\theta=0^\circ$, for a given time-bandwidth product specified with the parameter $\beta$:
%
\begin{align}
\beta = \frac{TB}{2},
\end{align}
%
where $T$ is the extent of the window in time and $B$ is its bandwidth. Adjusting $\beta$ changes the trade-off between mainlobe width and sidelobe level. At small values the windows approach the response of a rectangular window, and at large values ($>5$) the window converges to a Gaussian both in time and frequency. This class of windows is generally considered well suited for separating closely spaced sources with amplitudes of a high dynamic range~\cite{Harris1978}, they are easy to make, and they are optimal for any value of $\beta$.

Before we apply the window to the sensor data, we normalize it to ensure unit gain in the direction of interest:
%
\begin{align}
\w = \frac{\vec f}{\f\T\1} \quad\quad\text{where}\quad\quad \f =
\bmat{
f_0 \\ \vdots \\ f_{M-1}                                                           
}
\end{align}
%
Note that the normalization factor $\f\T\1$ is the reciprocal of the window's coherent gain. Since the signal-to-noise gain is constant for a given window, this normalization also proportionally increases the  incoherent noise gain.

\begin{align}
\w = \frac{\a\f}{\f\T\a} = 
\end{align}

\begin{align}
\a = \bmat{
1 \\
e^{-j\frac{md}{\lambda}\sin(\phi)} \\
\vdots\\
e^{-j\frac{(M-1)d}{\lambda}\sin(\phi)}
}
\end{align}

% \begin{align}
% \z = \w\H\a 
% \end{align}
